14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2020-04-01 rules/rules20.tex
ordered organizing team alphabetically

SMT-COMP 2020 is organized under the direction of the SMT Steering
Committee. The organizing team is
%
\todo{check your affiliations}
\begin{itemize}
\setlength{\itemsep}{0pt}
\item Haniel Barbosa~-- Universidade Federal de Minas Gerais, Brazil
\item \href{http://www.inf.usi.ch/postdoc/hyvarinen/}{Antti Hyvarinen}~--
		Universita della Svizzera italiana, Switzerland (chair)
\item Jochen Hoenicke~-- Universit\"at Freiburg, Germany
\end{itemize}
%
The competition chairs are responsible for policy and procedure decisions,
such as these rules, with input from the co-organizers.

@@

\header{Disclosure.}
%
\todo{add disclosure}
Antti Hyvarinen is part of the developing team of the SMT solver
OpenSMT~\cite{opensmt2}.
Jochen Hoenicke is part of the developing teams of the SMT solver
SMTInterpol~\cite{smtinterpol}.

>>>>

SMT-COMP 2020 is organized under the direction of the SMT Steering
Committee. The organizing team is
%
\todo{check your affiliations}
\begin{itemize}
\setlength{\itemsep}{0pt}
\item Haniel Barbosa~-- Universidade Federal de Minas Gerais, Brazil
\item Jochen Hoenicke~-- Universit\"at Freiburg, Germany
\item \href{http://www.inf.usi.ch/postdoc/hyvarinen/}{Antti Hyvarinen}~--
		Universita della Svizzera italiana, Switzerland (chair)
\end{itemize}
%
The competition chairs are responsible for policy and procedure decisions,
such as these rules, with input from the co-organizers.

@@

\header{Disclosure.}
%
\todo{add disclosure}
Jochen Hoenicke is part of the developing teams of the SMT solver
SMTInterpol~\cite{smtinterpol}.
Antti Hyvarinen is part of the developing team of the SMT solver
OpenSMT~\cite{opensmt2}.
